\def\version{1}
\problemname{Apple Delivery}

Ingrid, the apple farmer, has just harvested a huge amount of apples that she intends to give
to herself and her neighbours. Her neighbourhood can be represented by an infinite plane
where every point with integer coordinates contains exactly one house. Ingrid's house is
located at the origin $(0, 0)$. Ingrid has a special strategy when distributing apples. First, she
selects a list of non-negative integers $r_1, r_2, \cdots, r_N$. For each number in the list, she then
gives one apple to every house within radius $r_i$, i.e. every house whose coordinates satisfy $x^2+y^2 \leq r_i^2$
(including her own). That way, Ingrid's close neighbours get more apples than
her distant neighbours

Ingrid has just chosen the list of radii, but then a problem arose. When distributing apples
she always puts them in cube-shaped boxes with eight apples in each box. Therefore, it is
very important that the total number of apples distributed is a multiple of eight. Ingrid needs
to remove some radii from the list, so that the number of given apples becomes a multiple of
eight. It is always possible to do so, for example by removing all radii, but Ingrid does not
want to appear greedy so she wants to remove radii in a way that minimizes the number of
apples \textit{not} given among the ones she originally planned to give. Your task is to find this
minimum.

\section*{Input}
\noindent
The first row of input contains the integer, $N$ ($1 \leq N \leq 3 \cdot 10^5$), the number of radii.

The following line contains $N$ space-separated integers $r_1, r_2, \cdots, r_N$, the chosen radii.

\section*{Output}
\noindent
Output an integer, the minimum number of apples Ingrid can refrain from distributing by
removing radii from her list, in such a way that the total number of distributed apples
becomes a multiple of eight.

\section*{Points}
\noindent
Your solution will be tested on a set of test groups, each worth a number of points.
To get the points for a test group you need to solve all test cases in the test group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  Group & Points & Limits \\ \hline
  $1$    & $15$       &  $N \leq 10$, $r_i \leq 300$ for every $i$  \\ \hline 
  $2$    & $25$       &  $N \leq 3000$, $r_i \leq 1000$ for every $i$ \\ \hline
  $3$    & $15$       &  $r_i \leq 10^4$ for every $i$ \\ \hline
  $4$    & $45$       &  No additional constraints \\ \hline
\end{tabular}

\section*{Explanation of sample 1}
\noindent
Within a radius of: 0 there is 1 house, 1 there are 5 houses, and 2 there are 13 houses. In total
there are thus 26 houses within the radii. By removing the two radii 0 there are 24 remaining
houses.
